Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-11-28 doc/om-paper/paper.tex
commented stuff in the lemmas section.

\subsection{Invariants}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/proof-structure}
  \caption{Proof structure.}
  \label{fig:proof}
\end{figure}

@@

The lemmas are classified into five groups: calendar automata lemmas, abstract state machine lemmas, protocol behavior lemmas, majority vote lemmas, and fault model lemmas.

>>>>

\subsection{Invariants}
To make the proof scalable, we specify inductive invariants to be used by SAL's $k$-induction engine. The invariants are modular, focused on specific aspects of the model.

%% cal:
%%   cal_invt (-)

%% ASM:
%%   abstract_all (cal_invt, receiver_mode_invt)

%% faults:
%%   manifest_relay (-)
%%   symmetric_relay (-)
%%   fault_propagation (cal_invt)
%%   source_to_latch (fault_propagation)
%%   manifest_source (fault_propagation)

%% receiver:
%%   missing_buffer_size (cal_invt)
%%   receiver_mode_invt (missing_buffer_size)

%% voting:
%%   majority_vote_invt (receiver_mode_invt)
%%   exists_majority (receiver_mode_invt majority_vote_invt)

%% protocol: (everything :))
%%   validity
%%   agreement

\begin{figure}
  \centering
%%   \begin{tabular}{r|c|c|c|c|c|}
%%              & (a) Calendar & (b) ASM & (c) Protocol & (d) Voting & (e) Fault model \\
%%     \hline \hline
%%       Lemmas & 2            & 1       & 3            & 4          & 5 \\
%% Dependencies &              & (a), (d),         &              &            &   \\
%%   \end{tabular}
  %% \includegraphics[width=\textwidth]{figs/proof-structure}
  \caption{Invariant classification.}
  \label{fig:proof}
\end{figure}

The lemmas fall into five categories: calendar automata lemmas, abstract state machine lemmas, protocol behavior lemmas, majority vote lemmas, and fault model lemmas.

@@

@@
